Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru

### 2020-08-29 docs/enso_comp.Rmd
delete superfluous the

The experiment revealed that edaphic variables are conducive to vegetation development. 
The fertilized plots representing moderate El Niño episodes exhibited a slightly greater plant coverage than in their unfertilized counterparts (middle panel of Fig. \@ref(fig:irrigation)). 
Adding even more water revealed the true beneficial effects of fertilizing.
The fertilized plots simulating Super El Niño episodes showed a threefold increase in plant cover compared to their unfertilized counterparts (right panel of Fig. \@ref(fig:irrigation)).
Nevertheless, there was an upper limit regarding the beneficial effects of nutrient addition. 
Plant cover, and thus biomass production, stopped increasing or even decreased in the fertilized Super-El Niño plots after 8 March 2013, which corresponded to 1487 mm of irrigation and 200 kg ha^-1^ of NH~4~NO~3~.
Species richness followed a similar pattern -- highest numbers in species were recorded in the the fertilized Super-El Niño plots, though with just seven observed species the overall number remained low (Fig. \@ref(fig:spri-exp)).

>>>>

The experiment revealed that edaphic variables are conducive to vegetation development. 
The fertilized plots representing moderate El Niño episodes exhibited a slightly greater plant coverage than in their unfertilized counterparts (middle panel of Fig. \@ref(fig:irrigation)). 
Adding even more water revealed the true beneficial effects of fertilizing.
The fertilized plots simulating Super El Niño episodes showed a threefold increase in plant cover compared to their unfertilized counterparts (right panel of Fig. \@ref(fig:irrigation)).
Nevertheless, there was an upper limit regarding the beneficial effects of nutrient addition. 
Plant cover, and thus biomass production, stopped increasing or even decreased in the fertilized Super-El Niño plots after 8 March 2013, which corresponded to 1487 mm of irrigation and 200 kg ha^-1^ of NH~4~NO~3~.
Species richness followed a similar pattern -- highest numbers in species were recorded in the fertilized Super-El Niño plots, though with just seven observed species the overall number remained low (Fig. \@ref(fig:spri-exp)).
